manuscript_outline

### 2025-06-12 docs/manuscript/paper.Rmd
Edit case study section

There are numerous applications for effective value models and poikilotherms that expand well beyond the bounds of this manuscript. We provide examples spanning four taxonomic classes of pikilotherms in the table below of studies that could liekly be used to parameterize custom models using the `fit_model()` function from hatchR. These are a non-exhaustive search of the both peer-reviewed and grey literature, but demonstrate the wide taxonomic breadth that could be paired with the effective value approach. We provide case studies of how these data may be used to address a variety of questions, but expect applications to extend far beyond what we demonstrate here.

@@

: Sources for effective value parameterizations using `fit_model()` in hatchR. Represented are a broad range of taxa and some review studies which include numerous putative sources. @while2018 and @pritchard1987 not vetted for full functionality and equations would need to be reciprocated.

>>>>

The effective value modeling framework is broadly applicable across poikilothermic taxa and can be used to address a wide array of ecological, evolutionary, and management questions. While this manuscript focuses on three illustrative case studies, many additional opportunities exist. Below, we provide a non-exhaustive compilation of species for which thermal developmental data are available in the peer-reviewed or grey literature. These sources can be used to parameterize custom models via the `fit_model()` function in **hatchR**, allowing users to build tailored effective value models for diverse taxa. The examples span four taxonomic classes—amphibians, reptiles, insects, and crustaceans—and demonstrate the breadth of systems to which this approach can be applied. While the case studies we present here are intended as proof-of-concept, we anticipate that applications will continue to expand alongside the growing availability of temperature–development datasets.

@@

: Example sources for effective value parameterization using `fit_model()` in **hatchR.** This compilation spans amphibians, reptiles, aquatic and terrestrial insects, and decapod crustaceans. Some entries, such as @while2018 and @pritchard1987, represent broader reviews with multiple species and are flagged as not yet vetted for full reciprocal model implementation. Users may need to extract or adapt published equations to align with the effective value framework.
